\documentclass[Main]{subfiles}

\begin{document}

\chapter{Requirements traceability}


\section{Forward Traceability Matrices}


\begin{longtable}{p{0.07\textwidth} p{0.76\textwidth} p{0.11\textwidth}} \hline
SR & System Requirement & DDD \\\hline

SR-1 & The system shall be able to operate in manual mode which will dispense the program selected by the pilot. & DDD-1.5, DDD-1.6, DDD-2.1 \\

SR-2 & The system shall be able to operate in semi-automatic mode which will initiate an intelligent threat response upon consent from the pilot & DDD-1.5, DDD-1.6, DDD-2.1 \\

SR-3 & The system shall be able to operate in automatic mode which will initiate an intelligent threat response without pilot interaction & DDD-1.5, DDD-2.1 \\

SR-4 & The pod shall include a minimum of eight standard magazines & DDD-1.7 \\

SR-5 & The pod shall be able to dispense forwards, downwards and sideways & DDD-1.6 \\

SR-6 & Threats shall be transmitted to the aircraft mission computer in body frame format (relative to aircraft) for displaying purposes &  DDD-1.2\\

SR-7 & The system shall provide the aircraft mission computer with current status information & DDD-1.1, DDD-2.1, DDD-2.2 \\

SR-8 &  The system shall run built-in test and make the results available to the aircraft mission computer & DDD-1.4 \\

SR-9 & The system shall provide the aircraft intercom system audio cues and warnings & DDD-1.2 \\

SR-10 &  The system status on individual LRU level shall be provided by cockpit unit & DDD-1.3, DDD-1.4 \\

SR-11 & The cockpit unit shall be able to control power of dispensing system and MWS & DDD-1.8, DDD-2.3 \\

SR-12 & The system shall be able to dispense the payloads in a preloaded program &  \\

SR-13 & The payload patterns shall be programmable by the customer adjusting which payloads should be fired at which rate &  \\

SR-14 & The cockpit unit shall communicate with the mission computer via a MIL-STD-1553-B data bus &  \\

SR-15 & The system shall interface the aircraft intercom system via the MIL-STD-1553-B databus &  \\

SR-16 & The system shall provide a method of loading software to MWS &  \\

SR-17 & The cockpit unit shall communicate with the MWS via a MIL-STD-1553-B data bus &  \\

SR-18 & The system may not obstruct the current weapon systems physically & DDD-4.2 \\

SR-19 & The system response time for any given process must not exceed 5 ms, as not to hold up the mission computer. &  \\

SR-20 & The system shall include a hardware implemented safety interlock to prevent dispensing on ground &  \\

SR-21 & The system shall be able to erase sensitive data upon input from a discrete zeroize signal from the mission computer &  \\

SR-22 &  The pod structure shall remain intact when exposed to steady state acceleration levels of 5g fore 2.5g aft, 25g up, 11g down &  \\

SR-23 &  The pod shall be operational at temperatures of 95 degree Celsius on outer skin and 102 degree Celsius on leading edge for 25 minutes &  \\

SR-24 &  The pod shall be operational at temperatures of 134 degree Celsius on outer skin and 151 degree Celsius on leading edge for 3 minutes &  \\

SR-25 & The system shall be able to dispense a minimum of two payloads simultaneously  &  \\

SR-26 & The system can dispense a minimum of 20 payloads per second &  \\

SR-27 & The system shall provide the optimal coverage against	missile threats &  \\

SR-28 & The pod shall be mounted on the aircraft wing with standard T-hooks spaced by 13 inches & DDD-4.1 \\

SR-29 & The total weight of pod cannot exceed 270 kg  &  \\

SR-30 & The pod shall be mounted on the left-hand wing & DDD-4.1 \\

SR-31 & The power consumption of the pod shall not exceed 700W &  \\\hline

\caption{Forward Traceability Matrix}
\label{Tab:Forward}
\end{longtable}






\newpage
\section{Backward Traceability Matrices}

\begin{longtable}{l p{10.4cm} p{1.8cm} } \hline
System Reference & Functional Requirement & SR-ID\\\hline
\ref{DDD-11} & The mission computer shows which mode the system is in. & SR-7 \\

\ref{DDD-12} & The mission warning system provides a signal with a threat's location to the intercom system. & SR-6, 9 \\

\ref{DDD-13} & The mission computer shows how many flairs are left. & SR-7, 10\\

\ref{DDD-14} & The mission computer shows if all DSSs are available. & SR-8, 10\\

\ref{DDD-15} & The pilot can select mode with a physical unit -- either a button, flip switch or turn switch. & SR-1, 2, 3\\

\ref{DDD-16} & The pilot can select to fire flares of the selected pattern with a click of a button. & SR-1, 2, 5\\

\ref{DDD-17} & The maintenance crew can load flares form 8 hatches in the pod. & SR-4\\

\ref{DDD-18} & The pilot can turn off the power to the pod by clicking a button, flicking a switch or turning a switch. & SR-11\\

\ref{DDD-21} & The time it takes for the new mode to appear from the pilot selects a new mode shall be less than 30 ms. & SR-1, 2, 3, 7\\

\ref{DDD-22} & When flairs are fired the status sent to the Mission Computer shall be updated in less than 30 ms.& SR-7\\

\ref{DDD-23} & If the pilot turns on the pod after it has been disabled, the pod shall be ready in under 500 ms.& SR-11\\

\ref{DDD-31} & The selected mode shall be shown as text on the mission computer. & SR-7\\

\ref{DDD-41} &  The pod shall be mounted on the aircraft's left wing with standard T-hooks spaced by 13 inches. & SR-28, 30\\

\ref{DDD-42} & The pod must be no longer than 120 cm, no wider than 40 cm, no taller 40 cm and aerodynamic. & RFPS, SR-3.1, 18\\

\ref{DDD-43} & The pod shall be colored in light gray (FS 26373). & \\

\ref{DDD-44} & The pod shall only have marking of font size 60 pt Impact in black (\#000000). & \\
%
%\ref{F-1} & Accept User selection of dispensing pattern & SR-12\\
%
%\ref{F-2} & Accept User selection of operational mode. & SR-1,2,3\\
%
%\ref{F-3} & Receive dispensing pattern programs.& \\
%
%\ref{F-4} & Receive payload magazines. & SR-4\\
%
%\ref{F-5} & Distribute electricity. & SR-11\\
%
%\ref{F-6} & Support weight & \\
%
%\ref{F-7} & Detect threats& \\
%
%\ref{F-8} & Convert power AC/DC& \\
%
%\ref{F-9} & Ignite payloads& \\
%
%\ref{F-10} & Communicate threat info to F-16 Mission Computer& \\
%
%\ref{F-11} & Communicate threat info to F-16 Intercom System& \\
%
%\ref{F-12} & Receive "Fire" command& \\
%
%\ref{F-13} & Lock dispensing system& \\
%
%\ref{F-14} & Toggle pod power supply& \\
%
%\ref{F-15} & Validate "fire" command& \\


%\ref{ID-11} & The interface delivers power from the F-16 power supply to the SPS\_PCU.& \\
%
%\ref{ID-12} & The voltage is 115 VAC 400 Hz.& \\
%
%\ref{ID-13} & The SPS\_PCU will consume up to 250W. & \\
%
%\ref{ID-21} & All the interfaces named P\_2.1-2.4 are power interfaces from the F-16 power supply to each DSS. & \\
%
%\ref{ID-22} & The voltage is 115 VAC 400 Hz. & \\
%
%\ref{ID-23} & Each DSS will consume up to 126W. & \\
%
%\ref{ID-31} & All the interfaces named P\_3.1-3.4 are power interfaces from the SPS\_PCU to each DSS. & \\
%
%\ref{ID-32} & The voltage is 28V DC. & \\
%
%\ref{ID-33} & Each DSS consumes 3W. & \\
%
%\ref{ID-41} & The interface delivers power from the SPS\_PCU to the MWS. & \\
%
%\ref{ID-42} & The voltage is 28V DC. & \\
%
%\ref{ID-43} & The MWS will consume up to 85W. & \\
%
%\ref{ID-51} & The interface delivers power from the F-16 PCU to the SPS\_CU. & \\
%
%\ref{ID-52} & The voltage is 28V DC. & \\
%
%\ref{ID-53} & The SPS\_CU consumes up to 10W. & \\
%
%\ref{ID-61} & The interfaces CC\_1.1-1.4 are used for control of each DSS by the MWS. & \\
%
%\ref{ID-71} & The interfaces CC\_2.1-2.8 are used for igniting payloads by the DSS'. & \\
%
%\ref{ID-81} & The interface CC\_3.1 are used to turn on/off the power to the pod from the cockpit unit. & \\
%
%\ref{ID-91} &The interface is of type real-time data transfer and will have a maximal time of providing measured data in under 5 ms. & SR-19 \\
%
%\ref{ID-92} & The interface sets 3 different modes up to be chosen; automatic, semi-automatic and manual. & SR-1,2,3\\
%
%\ref{ID-93} & The interface provides two angles for each threat detected -- the first is 180 degree vertical, the second is 360 degree horizontal. & SR-6.7.9\\
%
%\ref{ID-94} & The interface provides a list of patterns the flares can be dispatched in.  & SR-7\\
%
%\newpage
%\ref{ID-95} & The interface provides a launch message for manual mode and semi-automatic mode to launch flares in the selected pattern. & \\

\\\hline
\caption{Backward Traceability Matrix}
\label{Tab:Backward}
\end{longtable}


\end{document}
