\documentclass[Main]{subfiles}
\begin{document}

\chapter{Requirements}

\section{Required states and modes}

\begin{enumerate}[{SR}-1]
\setcounter{enumi}{0}
\item The system shall be able to operate in manual mode which will dispense the program selected by the pilot (UR-12+13).\label{SR-1}

\item The system shall be able to operate in semi-automatic mode which will initiate an intelligent threat response upon consent from the pilot (UR-12+14).\label{SR-2}

\item The system shall be able to operate in automatic mode which will initiate an intelligent threat response without pilot interaction(UR-12+15).\label{SR-3}

\end{enumerate}

\section{System capability requirements}
\begin{enumerate}[{SR}-1]
\setcounter{enumi}{3}
\item The pod shall include a minimum of eight standard magazines(UR-1)\label{SR-4}

\item The pod shall be able to dispense forwards, downwards and sideways\fxnote{Hvordan vil I gøre det? UR-2}(UR-2) \label{SR-5}

\item Threats shall be transmitted to the aircraft mission computer in body frame format (relative to aircraft) for displaying purposes (UR-5).\label{SR-6}

\item The system shall provide the aircraft mission computer with current status information(UR-6).\label{SR-7}

\item The system shall run built-in test and make the results available to the aircraft mission computer (UR-6).\label{SR-8}

\item The system shall provide the aircraft intercom system audio cues and warnings.(UR-7)\label{SR-9}

\item The system status on individual LRU level shall be provided by cockpit unit (UR-10).\label{SR-10}

\item The cockpit unit shall be able to control power of dispensing system and MWS(UR-11).\label{SR-11}

\item The system shall be able to dispense the payloads in a preloaded program (UR-21). \label{SR-12}

\item The payload patterns shall be programmable by the customer adjusting which payloads should be fired at which rate(UR-21).\label{SR-13}
\end{enumerate}

\section{System external interface requirements}

\begin{enumerate}[{SR}-1]
\setcounter{enumi}{13}
\item The cockpit unit shall communicate with the mission computer via a MIL-STD-1553-B data bus (UR-41).\label{SR-14}

\item The system shall interface the aircraft intercom system via the MIL-STD-1553-B databus(UR-7).\label{SR-15}

\item The system shall provide a method of loading software to MWS (UR-16).\label{SR-16}
\end{enumerate}


\section{System internal interface requirements}

\begin{enumerate}[{SR}-1]
\setcounter{enumi}{16}
\item The cockpit unit shall communicate with the MWS via a MIL-STD-1553-B data bus (UR-40)\label{SR-17}

\end{enumerate}
%\section{System internal data requirements}

%\section{Adaptation requirements.}

\section{Safety requirements}
\begin{enumerate}[{SR}-1.]
\setcounter{enumi}{17}
\item The system may not obstruct the current weapon systems physically (UR-3).\label{SR-18}

\item The system response time for any given process may not exceed 5 ms (UR-3).\label{SR-19}

\item The system shall include a hardware implemented safety interlock to prevent dispensing on ground (UR-8).\label{SR-20}

\end{enumerate}


\section{Security and privacy requirements}

\begin{enumerate}[{SR}-1]
\setcounter{enumi}{20}
\item The system shall be able to erase sensitive data upon input from a discrete zeroize signal from the mission computer(UR-9).\label{SR-21}

\end{enumerate}


\section{System environment requirements}

\begin{enumerate}[{SR}-1]
\setcounter{enumi}{21}
\item The pod structure shall remain intact when exposed to steady state acceleration levels of 5g fore 2.5g aft, 25g up, 11g down (UR-30).\label{SR-22}

\item The pod shall be operational at temperatures of 95 degree Celcius on outer skin and 102 degree Celcius on leading edge for 25 minutes (UR-32).\label{SR-23}

\item The pod shall be operational at temperatures of 134 degree Celcius on outer skin and 151 degree Celcius on leading edge for 3 minutes (UR-33).\label{SR-24}

\end{enumerate}


%\section{Computer resource requirements}

\section{System quality factors}

\begin{enumerate}[{SR}-1]
\setcounter{enumi}{24}
\item The system shall be able to dispense a minimum of two payloads simultaneously (UR-20).\label{SR-25}

\item The system can dispense a minimum of 20 payloads per second.\label{SR-26}
\end{enumerate}

\section{Design and construction constraints}

\begin{enumerate}[{SR}-1]
\setcounter{enumi}{26}
\item The pod shall be mounted on the aircraft wing with standard T-hooks spaced by 13 inches (UR-42).\label{SR-27}

\item The total weight of pod cannot exceed 270 kg (UR-31).\label{SR-28}

\item The pod shall be mounted on the left-hand wing (UR-4).\label{SR-29}

\item The power consumption of the pod shall not exceed 700W (UR-43).\label{SR-30}
\end{enumerate}

%\section{Personnel-related requirements}
%
%\section{Training-related requirements}
%
%\section{Logistics-related requirements}
%
%\section{Packaging requirements}
%
%\section{Other requirements}

\end{document}