\documentclass[Main]{subfiles}
\begin{document}

\setcounter{chapter}{2}
\chapter{Test preparations}
This section describes the preparations needed to be done before going ahead with the tests.
Generally the test are to be done on fully assembled systems.

It is important that the tests are performed in the order they are described, to ensure validity of results.

\section{Test 1}
\textbf{Description: }\\
The test purely entail a weighing of the pod structure with all systems installed.

\textbf{Preparations: }\\
A complete pod needs to be assembled. 

It is not necessary to be connected to the cockpit unit or have final software running.

\textbf{Equipment:}
\begin{itemize}
\item One fully assembled pod, loaded with magazines
\item A weighing station capable of weighing at least 300 kg
\end{itemize}


\newpage
\section{Test 2}
\textbf{Description: }\\
The test validates all internal and external communication in the pod.
Further, it validates the power consumption of the pod.

\textbf{Preparations: }\\
A full system is assembled and connected to a test bench.
Access to a secure test facility needs to be obtained

\textbf{Equipment:}
\begin{itemize}
\item One fully assembled pod, with finished software and loaded with magazines
\item One cockpit unit
\item One test bench, simulating the interface of an F-16 aircraft
\item A secured testing area where dispensing of payloads i possible

\end{itemize}

\section{Test 3}
\textbf{Description: }\\
The test validates the sustainability of the pod, when exposed to acceleration.

\textbf{Preparations: }\\
A fully assembled pod is needed for this test. 

The pod shall be mounted in a centrifuge, when performing this test.

Software performing self-test of the pod is needed to validate the sustainability.

\textbf{Equipment:}
\begin{itemize}
\item One fully assembled pod, with accurately weighted dummy magazines
\item A centrifuge capable of generating at least 25 g
\item A test bench for self testing
\end{itemize}

\section{Test 4}
\textbf{Description: }\\
The test validates the sustainability of the pod, when exposed to high temperature.

\textbf{Preparations: }\\
The pod must be fully assembled for the test.
The self test systems and software must be available for post test diagnostics, but are not needed while heat is applied. 

\textbf{Equipment:}
\begin{itemize}
\item One fully assembled pod
\item A temperature test chamber
\item A test bench for self testing
\end{itemize}

\section{Test 5}
\textbf{Description: }\\
The test validates the integration of all system components.

\textbf{Preparations: }\\
A F-16 aircraft must be available to perform this test. The Cockpit Unit must be installed in the aircraft.
A fully assembled pod and complete software is needed.

\textbf{Equipment:}
\begin{itemize}
\item One fully assembled SPS system
\item One F-16 with a cockpit unit installed
\item Access to a test airport
\item A test pilot

\end{itemize}

\end{document}